Compilation and Backend-Independent Vectorization for Multi-Party Computation

### 2022-05-26 overleaf/tech_report/introduction.tex
Added link.

Our most important contribution is the implementation and evaluation of the compiler framework. We demonstrate expressivity of the source language by running the compiler on 16 programs with interleaved if- and for-statements; these include classical MPC benchmarks such as PSI and Biometric matching, as well as kMeans, Histogram, and other examples from the literature. 
Our compiler takes the routine and generated \emph{non-vectorized} MOTION code (from MPC Source on the picture above). It then optimizes MPC Source and generates 
\emph{vectorized} MOTION code (from Optimized MPC Source). We then run the two versions using Boolean GMW and the BMR protocols. (MOTION, which is designed for 
protocol mixing, supports Arithmetic GMW, however, it does not implement Comparison (CMP) and Multiplexing (MUX) as they would be rather inefficient.)
In our experiments vectorized code exhibits 24x improvement on average in circuit generation time for Boolean GMW (20x for BMR), 7x reduction 
in communication (2x), 97x reduction in number of gates (91x), 4x improvement in setup time (23x) and 21x improvement in online time (18x).
%\ana{Summarize results.}

>>>>

Our most important contribution is the implementation and evaluation of the compiler framework. 
We demonstrate expressivity of the source language by running the compiler on 16 programs with interleaved if- and for-statements; these include classical MPC benchmarks such as PSI and Biometric matching, as well as kMeans, Histogram, and other examples from the literature. 
Our compiler takes the routine and generated \emph{non-vectorized} MOTION code (from MPC Source on the picture above). It then optimizes MPC Source and generates 
\emph{vectorized} MOTION code (from Optimized MPC Source). We then run the two versions using Boolean GMW and the BMR protocols. (MOTION, which is designed for 
protocol mixing, supports Arithmetic GMW, however, it does not implement Comparison (CMP) and Multiplexing (MUX) as they would be rather inefficient.)
In our experiments vectorized code exhibits 24x improvement on average in circuit generation time for Boolean GMW (20x for BMR), 7x reduction 
in communication (2x), 97x reduction in number of gates (91x), 4x improvement in setup time in the LAN setting (23x) and 21x improvement in online time, again in the LAN setting (18x).
%\ana{Summarize results.}

The compiler can be found at~\url{https://github.com/milana2/ParallelizationForMPC} where~\url{https://github.com/milana2/ParallelizationForMPC/tree/gh-pages} shows experiments on small input sizes and details the different stages of the compiler.
